What is disputed on the web?

### 2010-01-29 papers/wicow_claimfinder/claimfinder.tex
Replaced Google counts with Yahoo counts

We search the web for patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$''. Figure~\ref{templates} shows a subset of the patterns that we search for. For each pattern, we show the number of times that Google estimates that the pattern appears on the web.

@@

\todo{Give some stats about our patterns}
\todo{Use Yahoo BOSS counts rather than Google}
\note{It seems silly to use Google's counts for these when we are using Yahoo BOSS. Someone should write a script to re-generate this table using Yahoo BOSS counts.}

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count\footnotemark} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
   \hline
   \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    243,000,000 & it is not the case that \\
    30,700,000 & it is not true that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    9,960,000 & into believing that \\
    8,970,000 & disagree with the claim that \\
    7,190,000 & the mistaken belief that \\
    6,160,000 & disagree with the assertion that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,700,000 & mistaken belief that \\
    3,600,000 & the false belief that \\
    3,440,000 & the deceit that \\
    2,290,000 & cast doubt on the claim that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    1,630,000 & mistakenly believe that \\
    1,090,000 & false claim is that \\
    1,290,000 & the hoax that \\
    698,000 & absurdity of the claim that \\
    681,000 & falsely claimed that \\
    659,000 & no longer think that \\
%     654,000 & urban legend that \\
%     530,000 & the absurd idea that \\
%     373,000 & erroneously believe that \\
%     334,000 & the fabrication that \\
%     103,000 & falsely claiming that \\
%     140,000 & erroneous belief that \\
%     72,600 & falsely claim that \\
%     152,000 & bogus claim that \\
%     224,000 & the fantasy that \\
%     171,000 & incorrectly claim that \\
%     249,000 & incorrectly claimed that \\
%     232,000 & incorrectly believe that \\
%     98,900 & stupidly believe that \\
%     429,000 & falsely believe that \\
%     376,000 & wrongly believe that \\
%     189,000 & falsely suggests that \\
%     280,000 & falsely claims that \\
%     148,000 & false claim that \\
%     136,000 & no longer believe that \\
%     65,300 & urban myth that \\
%     59,500 & falsely stated that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}
\end{center}
\end{figure}

>>>>

We search the web for patterns that indicate that a claim is disputed, such as ``false claim that $X$'' or or ``it is not true that $X$''. Figure~\ref{templates} shows a subset of the patterns that we search for. For each pattern, we show the number of times that Yahoo estimates that the pattern appears on the web.

@@

\todo{Give some stats about our patterns}

@@

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|ll|}
    \hline
    {\bf Yahoo Count\footnotemark} & {\bf Template}\\ 
    \hline
        \multicolumn{2}{|c|}{\it Something that could be challenged}\\
        570,000,000 & think that \\
        495,000,000 & believe that \\
        145,000,000 & idea that \\
        101,000,000 & claim that \\
       \hline
       \multicolumn{2}{|c|}{\it Something others believe}\\
        40,100,000 & claiming that \\
        30,600,000 & the belief that \\
        28,600,000 & believing that \\
        11,700,000 & who believe that \\
        8,400,000 & who think that \\
        \hline
        \multicolumn{2}{|c|}{\it Something false}\\
        5,790,000 & the myth that \\
        3,260,000 & into believing that \\
        1,690,000 & the lie that \\
        1,410,000 & it is not true that \\
        1,220,000 & the delusion that \\
        1,140,000 & the misconception that \\
        995,000 & mistaken belief that \\
        676,000 & the mistaken belief that \\
        593,000 & mistakenly believe that \\
        583,000 & the fantasy that \\
        501,000 & it is not the case that \\
        459,000 & false claim that \\
        405,000 & the fallacy that \\
        351,000 & falsely claimed that \\
        264,000 & urban legend that \\
        250,000 & no longer believe that \\
        216,000 & the false belief that \\
        215,000 & falsely claiming that \\ 
        178,000 & falsely believe that \\
        171,000 & bogus claim that \\
        163,000 & erroneous belief that \\
        154,000 & the deception that \\
        147,000 & the misunderstanding that \\
        135,000 & urban myth that \\
    %    131,000 & wrongly believe that \\
    %    126,000 & falsely claim that \\
    %    109,000 & erroneously believe that \\
    %    101,000 & falsely claims that \\
    %    83,900 & incorrectly believe that \\
    %    83,200 & no longer think that \\
    %    82,400 & falsely stated that \\
    %    79,200 & the absurd idea that \\
    %    74,100 & the hoax that \\
    %    41,500 & the deceit that \\
    %    23,700 & incorrectly claimed that \\
    %    21,900 & disagree with the claim that \\
    %    15,900 & falsely suggests that \\
    %    15,300 & disagree with the assertion that \\
    %    14,200 & the fabrication that \\
    %    9,640 & incorrectly claim that \\
    %    2,110 & cast doubt on the claim that \\
    %    2,080 & absurdity of the claim that \\
    %    1,820 & false claim is that \\
    %    1,750 & stupidly believe that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Yahoo's rough estimate of how many times each one appears on the web}
\end{center}
\end{figure}
